---
fontsize: 10pt
geometry: margin=0.5in
output:
  pdf_document:
    toc: yes
    toc_depth: '3'
---

# This file is not currently functional! Please check back later.

The purpose of this file is to re-run all existing code to ensure all of your analyses are up to date and consistent with one another.  Note that this will likely need some tweaking as you create more files etc.  As long as the files can be run in numerical order (e.g. 1a, 1b, 2a etc.) and experiments start with "Experiment[1-9]", this should be functional.

```{r, echo=F}
source("~/Svelte-Analysis/1_CoreCode/1a_Settings.R") # All settings needed
```

---
title: "`r ProjectName` Aggregator"
author: "`r AuthorName`, `r AuthorAffiliation`"
date: "`r format(Sys.time(),format="%B %d, %Y")`"
---

\newpage


=======================================

# Information 

The purpose of this document is to aggregate the knitr output from any and all files that you want to run.

## Libraries and functions

Load all of the libraries needed and supplemental functions.

```{r, echo=rmd_all, autodep=TRUE}
#source("ProjectName_PackagesFunctions.R") # All packages and functions needed
```

## Define Rmd files to run.

```{r, eval=T} 
# For example, if you want to re-run all code to transform raw data to an analsis datafile, you would run the code below.
# setwd(project_folder)
# ksource("LoadMerge.Rmd") # Load all data and merge together
# setwd(project_folder)
# ksource("FilterSave.Rmd") # Filter and save deidentified data - Eric stopped fixing here
# setwd(project_folder)
# ksource("NewItems.Rmd") # Create new items - this should be moved after FilterSave...



#ksource("ExploratoryAnalysis.Rmd")
```


