---
fontsize: 10pt
geometry: margin=0.5in
output:
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r, include=F}
source("0_Header.R") # Load Header

### Put any temporary functions here (to be put into function files later)
```

---
title: "`r ProjectName` - Load & Merge Files"
author: "`r AuthorName`, `r AuthorAffiliation`"
date: "`r format(Sys.time(),format="%B %d, %Y")`"
---

\newpage


=======================================

# Information 

The purpose of this document is to load and merge all identifiable files.  If no merging or deidentification is require, you may only need to read the files in this document.

## Load all files

Here we load all files.

```{r loadFiles,cache={{rmd_cache}}, echo={{rmd_all}}, message={{rmd_all}}}
setwd(deidentified_data_folder) # Set where data is coming from

df1 <- read.csv("file1.csv",stringsAsFactors=F)
df2 <- read.csv("file1.csv",stringsAsFactors=F)
```

## Fix up column names


## Fix up data for merging

You may need to fix up the data or create columns for accurate merging. Do so here.

```{r checkMerge,cache={{rmd_cache}}, echo={{rmd_all}}, message={{rmd_all}}}
```

## Ensure the files can be merged.

Ensure colnames are similar and/or dimensions of files can be combined.

```{r checkMerge,cache={{rmd_cache}}, echo={{rmd_all}}, message={{rmd_all}}}
# The names are identical in session 1
table(names(df1) == names(df2))
dim(df1)
dim(df2)
```



### Combine the files

```{r mergeFiles,cache={{rmd_cache}}, echo=FALSE, message={{rmd_all}}}
# Combine the conditions
df <- rbind.fill(df1,df2) # combining similar datasets
df <- full_join(d1, d2, by= "id") # combining mostly unique data across files

df_orig <- df # designate as d
df <- smart_cast_numeric(df) # make numeric rows as.numeric
```

### Determine how many were successfully merged and other metrics
```{r mergeInfo,cache={{rmd_cache}}, echo={{rmd_all}}, message={{rmd_all}}}

#Write Function
```

### Write any intermediate files as needed
```{r, echo={{rmd_all}}}

# write.csv(df,paste0(deidentified_data_folder,"/fulldata.csv",row.names=F)
```
