---
fontsize: 10pt
geometry: margin=0.5in
output:
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r, echo=F}
source("1_CoreCode/1a_Settings.R") # All settings needed
source("1_CoreCode/1b_PackagesFunctions.R") # All Packages and Functions
```

---
title: "`r ProjectName` Load & Merge Files"
author: "`r AuthorName`, `r AuthorAffiliation`"
date: "`r format(Sys.time(),format="%B %d, %Y")`"
---

\newpage


=======================================

# Information 

The purpose of this document is to load and merge all identifiable files.  If no merging or deidentification is require, you may only need to lead the files in this document.

## Load all files

Here we load all files.

```{r loadFiles,cache={{rmd_cache}}, echo={{rmd_all}}, message={{rmd_all}}}
setwd(deidentified_data_folder) # Set where data is coming from

df1 <- read.csv("file1.csv",stringsAsFactors=F)
df2 <- read.csv("file1.csv",stringsAsFactors=F)
```

## Ensure the files can be merged.

Ensure colnames are similar and/or dimensions of files can be combined.

```{r checkMerge,cache={{rmd_cache}}, echo={{rmd_all}}, message={{rmd_all}}}
# The names are identical in session 1
table(names(df1) == names(df2))
dim(df1)
dim(df2)
```

## Fix up data

You may need to fix up the data for accurate merging. Do so here.

```{r checkMerge,cache={{rmd_cache}}, echo={{rmd_all}}, message={{rmd_all}}}
```

### Combine the files

```{r mergeFiles,cache={{rmd_cache}}, echo=FALSE, message={{rmd_all}}}
# Combine the conditions
df <- rbind.fill(df1,df2) # combining similar datasets
df <- full_join(d1, d2, by= "id") # combining mostly unique data across files

df_orig <- df # designate as d
df <- smart_cast_numeric(df) # make numeric rows as.numeric
```

### Determine how many were successfully merged and other metrics
```{r mergeInfo,cache={{rmd_cache}}, echo={{rmd_all}}, message={{rmd_all}}}
```

### Write any intermediate files as needed
```{r, echo={{rmd_all}}}

# write.csv(df,paste0(deidentified_data_folder,"/fulldata.csv",row.names=F)
```
