---
fontsize: 10pt
geometry: margin=0.5in
output:
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r, include=F}
source("0_Header.R") # Load Header

### Put any temporary functions here (to be put into function files later)
```

---
title: "`r ProjectName` Demographics and Methods"
author: "`r AuthorName`, `r AuthorAffiliation`"
date: "`r format(Sys.time(),format="%B %d, %Y")`"
---

\newpage

=======================================

# Information 

Here we get demographic information, scale information, manipulation checks, etc. to ensure the data is cleaned and our main analyses are reasonable.

## Load the data
```{r}
# by csv or Rdata
# df <- read.csv(paste0(deidentified_data_folder,"file.csv"), stringsAsFactors=FALSE)

# load("Support/Rdata/RELMS_201516_cleaned_dfs.Rdata")
```

## Analyze the data

This is going to look pretty different for each project, but it should follow the same basic structure of clear headings.  A good way to do that is organize by test, question, or hypothesis

## H.1) My first hypothesis is X

```{r}

```


## Write files for reports
```{r}
# save(list=c("df"), file = "Support/Rdata/Exp1.3b.Rdata")
```
