---
fontsize: 10pt
geometry: margin=0.5in
output:
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r, echo=F}
source("1_CoreCode/1a_Settings.R") # All settings needed
source("1_CoreCode/1b_PackagesFunctions.R") # All Packages and Functions
# Requires 2a_LoadMerge file

```

---
title: "`r ProjectName` New Items"
author: "`r AuthorName`, `r AuthorAffiliation`"
date: "`r format(Sys.time(),format="%B %d, %Y")`"
---

\newpage

=======================================

# Information 

In this file, we create new columns.


Note: Many of the automatic functions included depend on having a session designation attached, with cols labeled, for example, "s1.myscale_1".  
The prefix "s1" indicates session 1, and the suffix "_1" indicates the first item of myscale.  Note that you can add this prefix to any dataset for these functions to work without modification.


### Create new columns

Here we create new columns that come in handy when graphing and doing data analysis.

```{r newcols, echo={{rmd_data}}, cache={{rmd_cache}}, message={{rmd_all}}, warning={rmd_all}} 
```

### Create new scales and composites (Automatic)

```{r newcols, echo={{rmd_data}}, cache={{rmd_cache}}, message={{rmd_all}}, warning={rmd_all}} 
```

### Create new scales and composites (Manual)

Some scales need to be made manually, due to inconsitent coding or subscales

```{r newcols, echo={{rmd_data}}, cache={{rmd_cache}}, message={{rmd_all}}, warning={rmd_all}} 
```
